---
title: " Wine Quality Report"
output: html_document
knit: (function(input, ...) {
    rmarkdown::render(
      input,
      output_dir = "../"
    )
  })

## Data
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyr)
library(janitor)
library(here)
library(readxl)
library(tidyverse)
library(GGally)
library(corrplot)
library(ggplot2)
```
## Introduction
This report analyze the red wine quality dataset in order to get insight in understand the data patterns.
## DATA
We explore the red wine quality dataset from UCIML which consists of twelve features that will be analysed.

```{r}
myData <- read_csv(here("data/winequality-red.csv"))
```


| Features      | Description |
| ----------- | ----------- |
| fixed acidity      | This feature refers to unevaporated readily acids involved with the wine, which are (fixed or nonvolatile) |
| volatile acidity  | This feature refers to the wine's acetic acid amount.   |
| citric acid   | This feature refers to the small quantity of citric acid, which adds good freshness and flavor to wines.  |
| residual sugar   | This feature refers to the sugar remaining after fermentation stops quantity. |
| chlorides | This feature refers to the wine's salt amount. |
| free sulfur dioxide   | This feature is used to prevent the oxidation of the wine and refers to the SO2 existing in equilibrium between molecular SO2.  |
| total sulfur dioxide | This feature refers to SO2, which is the amount of sulfur dioxide. |
| density | This feature refers to the density percent of alcohol and sugar. |
| pH | This feature refers to the acidic or basic of the wine, which is very acidic in the 0 and very basic in the to 14. ( pH scale should be between 3-4 in wines)  |
| sulphates | This feature refers to contribute to sulfur dioxide gas (S02), which works as an antimicrobial and antioxidant |
| alcohol  | This feature refers to wine' alcohol percent. |
| quality  | This feature refers to wine quality, which is between 0 and 10 |



## EDA
This section exploratory data analysis will be performed. 
Scatterplot matrices are a great way to roughly determine if you have a linear correlation between multiple variables. Therefore, We plot the data in the Scatterplot Matrix to present the data features as follows: 

```{r}
plot(myData)
```


A correlation heatmap is a graphical representation of a correlation matrix representing the correlation between different features 
Therefore, the following plot presents the data features in the heatmap correlation. 

```{r}
corrplot(cor(myData))
```


Moreover,  we distribute the wine quality ratings as follows: 

```{r}
ggplot(myData,aes(x=quality))+geom_bar(stat = "count",position = "dodge")+ scale_x_continuous(breaks = seq(3,8,1))+
ggtitle("The Quality Ratings of Red Wine")+
theme_classic()
```


## Conclusin 
To summarize, we found that red wine quality is substantially linked with alcohol and volatile acidity in our exploratory research.


